Leveraging the VTA-TVM Hardware-Software Stack \\for FPGA Acceleration of 8-bit ResNet-18 Inference

### 2018-06-13 dissemination.publication/9375838469ad4029/paper.tex
formatting
minor clean up

@@

\begin{verbatim}
$ ck install package:lib-tvm-runtime-master --env.PACKAGE_GIT_CHECKOUT=e4c2af9abdcb3c7aabafba8084414d7739c17c4c
\end{verbatim}

@@

\begin{verbatim}
$ ck install package:lib-tvm-master-cpu --env.PACKAGE_GIT_CHECKOUT=e4c2af9abdcb3c7aabafba8084414d7739c17c4c
\end{verbatim}

>>>>

\usepackage{fancyvrb}
\DefineVerbatimEnvironment{verbatim}{Verbatim}{xleftmargin=.5in}

@@

\begin{verbatim}
$ ck install package:lib-tvm-runtime-master \
   --env.PACKAGE_GIT_CHECKOUT=e4c2af9abdcb3c7aabafba8084414d7739c17c4c
\end{verbatim}

@@

\begin{verbatim}
$ ck install package:lib-tvm-master-cpu \
   --env.PACKAGE_GIT_CHECKOUT=e4c2af9abdcb3c7aabafba8084414d7739c17c4c
\end{verbatim}
